Results

### 2024-08-08 analysis/results.Rmd
tmp save

wos_active_jns <- wos_hybrid_jns |>
  filter(pubyear %in% 2019:2023)

@@

# wos core 
wos_active_core <- wos_active_jns |>
  filter(item_type %in% c("Article", "Review"))
```

@@

scp_active_jns <- scp_hybrid_jns |>
  filter(pubyear %in% 2019:2023)

@@

# Plot Journals Five Years Period
upset(fromList(item_view_df), order.by = "freq")
```

@@

upset(fromList(jn_list_with_oa), order.by = "freq")
```
### Item level

>>>>

wos_active_jns <- wos_hybrid_jns |>
  # use online first, if available
  mutate(online_year = lubridate::year(wos_pubdate_online)) |>
  mutate(pub_year = ifelse(!is.na(online_year), online_year, pubyear)) |>
  filter(pub_year %in% 2019:2023)

@@

# wos core 
wos_active_core <- wos_active_jns |>
  filter(grepl("Article|^Review$", item_type))
```

@@

scp_active_jns <- scp_hybrid_jns |>
   # use online first, if available
  mutate(pub_year = ifelse(!is.na(first_pubyear), first_pubyear, pubyear)) |>
  filter(pub_year %in% 2019:2023)

@@

# Plot Journals Five Years Period
UpSetR::upset(UpSetR::fromList(item_view_df), order.by = "freq")
```

@@

upset(fromList(jn_list_with_oa), order.by = "freq")
```

#### Compose a complex upset

```{r upset_data}
cr_active_upset <- cr_df |>
  filter(issn_l %in% active_jns$issn_l) |>
  group_by(issn_l) |>
  summarise(n_cr = n_distinct(doi)) |>
  mutate(crossref = TRUE)
wos_active_upset <- wos_active_core |>
  group_by(issn_l) |>
  summarise(n_wos = n_distinct(item_id)) |>
  mutate(wos = TRUE)
scp_active_upset <- scp_active_core |>
  group_by(issn_l) |>
  summarise(n_scp = n_distinct(item_id)) |>
  mutate(scopus = TRUE)

jn_upset_ <- dplyr::full_join(cr_active_upset, wos_active_upset, by = "issn_l") |>
  dplyr::full_join(scp_active_upset, by = "issn_l") |>
  mutate(across(c(crossref, wos, scopus), ~replace_na(.x, FALSE))) |>
  # Journal 5-years article volume
  mutate(n = case_when(!is.na(n_cr) ~ n_cr, !is.na(n_scp) ~n_scp, TRUE ~ n_wos))

# add year
jn_age <- jn_ind |> 
  mutate(cr_year = as.numeric(as.character(cr_year))) |> 
  filter(cr_year %in% 2019:2023) |>
  group_by(issn_l) |>
  summarise(min_year = min(cr_year),
            max_year = max(cr_year)) |>
  mutate(jn_age = max_year - min_year + 1)

jn_upset <- jn_upset_ |>
  inner_join(jn_age, by = "issn_l")
library(ComplexUpset)

ComplexUpset::upset(
  jn_upset,
  c("crossref", "wos", "scopus"),
  base_annotations = list(
    `Journals` = (
      intersection_size() +
        scale_y_continuous(labels =  scales::number_format(big.mark = ","))
    )
  ),
  annotations = list(
    'Article Volume' = (
      ggplot(jn_upset, aes(x = intersection, y = n)) +
        geom_boxplot(outliers = FALSE) +
        scale_y_log10(labels =  scales::number_format(big.mark = ",")) 
    ),
    # journal age, not very useful
    'Journal age' = (
      ggplot(jn_upset, aes(x = intersection, y = jn_age)) +
         geom_violin())
    )
  )
```

What is the age of the journals?

```{r journal_age}
jn_age <- jn_ind |> 
  mutate(cr_year = as.numeric(as.character(cr_year))) |> 
  filter(cr_year %in% 2019:2023) |>
  group_by(issn_l) |>
  summarise(min_year = min(cr_year),
            max_year = max(cr_year)) |>
  mutate(jn_age = max_year - min_year + 1) 
```
